### 2025-07-09 factor-analysis.qmd
20250708 - track chunk execution times
20250708 - tweaks

@@

```{r}
dataForFA <- dataMerged
dataForFA[faVars] <- scale(dataForFA[faVars])
```

@@

cfaModel1_fit <- lavaan::cfa(
  cfaModel1_syntax,
  data = dataForFA,
  missing = "ML",
  estimator = "MLR",
  std.lv = TRUE,
  cluster = "player_id",
  em.iter.max = 2000000)
```

>>>>

#### Subset Data {#sec-pcaPrepareDataSubset}

```{r}
dataMerged_subset <- dataMerged %>% 
  filter(!is.na(player_id))
```

@@

```{r}
dataForFA <- dataMerged_subset
dataForFA[faVars] <- scale(dataForFA[faVars])
```

@@

cfaModel1_fit <- lavaan::cfa(
  cfaModel1_syntax,
  data = dataForFA,
  missing = "ML",
  estimator = "MLR",
  std.lv = TRUE,
  cluster = "player_id",
  em.h1.iter.max = 2000000)
```
